### 2019-08-27 reports/paper1/paper.tex
Add BW method, one less parameter in Boxplots, paper uses linear shading correction

\title{Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter}
\date{2019}
\author[1]{S.E.~Lo}
\author[2]{J.W.~Warnett}
\author[2]{G.J.~Gibbons}
\author[2]{M.A.~Williams}
\author[3]{T.E.~Nichols}
\author[1,*]{J.A.~Brettschneider}
\affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
\affil[2]{Warwick Manufacturing Group, University of Warwick, Coventry, CV4 7AL, UK}
\affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
\affil[*]{Corresponding author: julia.brettschneider@warwick.ac.uk, +442476574812}

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using 20 black (\SI{0}{\kilo\volt}) and 20 white images (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

19 randomly selected projections, of the test sample, were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated white image.

@@

For each position $(x,y)$, a test statistic was calculated
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection. The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link. The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}). These replicated projections were manually segmented so that only pixels which represent the test sample were used. This provided variance-mean data, where each pixel is a data point, which was used to fit the variance model. The variance was predicted using the grey value in the simulated projection as the predictor variable.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD model of the test sample with voids. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.eps}
  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
  \label{fig:inference_segmentFurther}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{Area under the ROC curve (AUC) and statistical errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect for Various kernel radiuses. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was conducted at the 5\% FDR level. The box plots summarise the 100 repeated measurements of the simulation.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

>>>>

\title{Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter}
\date{2019}
\author[1]{S.E.~Lo}
\author[2]{J.M.~Warnett}
\author[2]{G.J.~Gibbons}
\author[2]{M.A.~Williams}
\author[3]{T.E.~Nichols}
\author[1,*]{J.A.~Brettschneider}
\affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
\affil[2]{Warwick Manufacturing Group, University of Warwick, Coventry, CV4 7AL, UK}
\affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
\affil[*]{Corresponding author: julia.brettschneider@warwick.ac.uk, +442476574812}

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{seibert1998flat} was applied to each projection using 20 greyscale projections, with powers \SI{0}{\kilo\volt}, \SI{5}{\kilo\volt}, \SI{10}{\kilo\volt}, \SI{15}{\kilo\volt} and \SI{20}{\kilo\volt}, to remove intensity influences and variations in pixels of the detector.

19 randomly selected projections, of the test sample, were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated greyscale projections.

@@

For each position $(x,y)$, a test statistic was calculated
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection. The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{ma2012varaince, yang2010noise}. A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link. The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}). These replicated projections were manually segmented so that only pixels which represent the test sample were used. This provided variance-mean data, where each pixel is a data point, which was used to fit the variance model. The variance was predicted using the grey value in the simulated projection as the predictor variable.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/TestObjectBW.png}
  \caption{The CAD model of the test sample with voids. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminatedBW.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/segmentBW.eps}
  \caption{The $z$ image was segmented further into 7 segments shown by the dashed lines.}
  \label{fig:inference_segmentFurther}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_rocBW.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1BW.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2BW.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdrBW.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{Area under the ROC curve (AUC) and statistical errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect for Various kernel radiuses. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was conducted at the 5\% FDR level. The box plots summarise the 100 repeated measurements of the simulation.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMeanBW.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStdBW.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted white positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

### 2019-08-27 reports/thesis/book.tex
Add BW method, one less parameter in Boxplots, paper uses linear shading correction

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This resulted in a linear relationship between the mean and variance of the grey value in the projection, which was used for variance prediction and to quantify the uncertainty. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model.

>>>>

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This resulted in a linear relationship between the mean and variance of the grey value in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma distributed generalised linear model was fitted and used for variance prediction and to quantify the uncertainty.
